---
title: "Erika_notes"
format: html
---

## How to push a locally created ***R*** project to ***GitHub***]

in RStudio > File > New Project > New Directory > New Project > Directory name: <Repository name>, check "Create a git repository"

### Configure a GitHub Personal Access Token (PAT):

Login to your GitHub account and go to the Settings tab. Then select Developer Settings and then Personal Access Tokens.
Select Generate new token and give it a nickname that reminds you of the intended purpose (e.g., “Access GitHub from RStudio”).
Pick a scope that confers the privileges you need, e.g., repo, and then press the green “Generate Token” button.
The PAT will be displayed. It is a string of 40 random letters and digits. Copy this string to the clipboard.
Enter the PAT in your “.Renviron” file as a line that looks like this: `GITHUB_PAT=<your token>` (not in quotation marks).
The “.Renviron” file is a hidden file located in a user’s home directory that can be used to set some default parameters for new R sessions. You can load and edit this with a function from the {usethis} package. At a console prompt, type `usethis::edit_r_environ()`. Your “.Renviron” file should open up in the RStudio editor. Add your the `GITHUB_PAT=<your token>` line as above, save and close the file. Be sure to put a line break at the end!
Restart R (Session > Restart R in the RStudio menu bar), as environment variables are loaded from “.Renviron” only at the start of an R session. Check that the PAT is now available: `Sys.getenv("GITHUB_PAT")`. You should see your PAT print to screen.

```{r}
install.packages('usethis')
librar(usethis)
# use_git_config(user.name = "ecarlson5683", user.email = "ecarlson5683@gmail.com") #done previously
use_git()
usethis::use_github(protocol="https")
```

First attempt, got an error message
```{r}
> usethis::use_github(protocol="https")
✔ Setting active project to '/Users/erc2866/Development/Repos/exercise-2b'
Error in `git_default_branch()`:
! Can't determine the local repo's default branch.
Run `rlang::last_trace()` to see where the error occurred.
```

Then realized 1 commit is required prior to pushing a locally created repository up, so I did that and it worked

The `echo: false` option disables the printing of code (only output is displayed).
